### 2025-02-13 README.Rmd
fix readme links

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

@@

```{r}
# install.packages("speff2trial")
library(speff2trial)

@@

```{r fig.width=12}
library(causalDT)

@@

```{r}
# selecting between causal forest versus rboost
rboost_cdt <- causalDT(
  X = as.matrix(X), Y = Y, Z = Z,
  teacher_model = rboost
)
plot_jaccard(`Causal Forest` = causal_forest_cdt, `Rboost` = rboost_cdt)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = file.path("causalDT", "man", "figures", "README-")
)
```

@@

```{r load-data}
# install.packages("speff2trial")
library(speff2trial)
library(dplyr)

@@

```{r causalDT, fig.width=12}
library(causalDT)

@@

```{r jaccard}
# selecting between causal forest versus rboost
rboost_cdt <- causalDT(
  X = as.matrix(X), Y = Y, Z = Z,
  teacher_model = rboost
)
plot_jaccard(`Causal Forest` = causal_forest_cdt, `Rboost` = rboost_cdt)
```
